---
title: "Critical Role Subtitles"
output: rmarkdown::github_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.path = "output/README_figs/"
)
```


# To Do:
  - blogpost in Rmarkdown and Pictures included
  - Model Fitting:
  
## Data Cleaning:
```{r cleaning, eval=FALSE, warning=FALSE}
# run script
source("./scripts/data_cleaning.R", local = knitr::knit_global())

# Note: E031-2,E035-2,E082,E113-1,E113-2 have been run once through
# error fixing* with Subtitle editor** in Ubuntu 20.04. This is needed as
# the files contain formatting errors, which renders them unusable for the 
# following analysis. 
# The original files are included in the same folder and are named as follows:
# 'original_C1E031-1_FINAL.srt'
# * Tools -> Error checking -> Error -> Try to fix all 
# ** (install via 'sudo apt install subtitleeditor' on ubuntu)
```  

## Create Data for Visualization
```{r descriptive_analysis, eval=FALSE, warning=FALSE}
# run script
source("./scripts/data_descriptive_analysis.R", local = knitr::knit_global())
```  

## Descriptive Analysis:
```{r descriptive_analysis, eval=FALSE, warning=FALSE}
# run script
source("./scripts/descriptive_analysis.R", local = knitr::knit_global())
```  

## Machine Learning:
```{r descriptive_analysis, eval=FALSE, warning=FALSE}
# run script
source("./scripts/machine_learning.R", local = knitr::knit_global())
```  

Visualisation:
  - tf_df
  - normalize sentiment
  - everything in one data frame for actors
  - check if time in MS or SEC
  - questions: where is episode 115? Where is arc "End"?
  - check episode numbers(12 = not 12 as this is dungeon master tips?)


Models to tune:
  - For accuracy:
      - Kernel SVM
      - random forest
      - gradient boost
      - neural network
  - for speed
      - decision tree
      - naive Bayes
      - linear SVM
      - knn
  - for completion
      - lasso etc.

Links to looks at:
https://smltar.com/

[Model Monitoring with R Markdown, pins, and RStudio Connect | RStudio Blog](https://blog.rstudio.com/2021/04/08/model-monitoring-with-r-markdown/)

https://www.youtube.com/watch?v=yKs6msnw9m8

[Research | Susan Athey](https://athey.people.stanford.edu/research#econometric)

[GitHub - grf-labs/grf: Generalized Random Forests](https://github.com/grf-labs/grf)

https://juliasilge.shinyapps.io/learntidytext/

https://www.youtube.com/watch?v=ntk_1xLQBwo

[Predicting Housing Prices with Natural Language Processing NLP and Tidymodels | R-bloggers](https://www.r-bloggers.com/2021/02/predicting-housing-prices-with-natural-language-processing-nlp-and-tidymodels/)

[RStudio AI Blog: State-of-the-art NLP models from R](https://blogs.rstudio.com/ai/posts/2020-07-30-state-of-the-art-nlp-models-from-r/)

[GitHub - thllwg/tpotr: An R-Wrapper for the Python Automated Machine Learning tool that optimizes machine learning pipelines using genetic programming (TPOT)](https://github.com/thllwg/tpotr)

[Extract YouTube video statistics based on a search query | by Rare Loot | Medium](https://rareloot.medium.com/extract-youtube-video-statistics-based-on-a-search-query-308afd786bfe)

[TidyTuesday: NLP Modeling with TidyModels and Keras - YouTube](https://www.youtube.com/watch?v=0aN5Io0rJZI)

- https://docs.h2o.ai/h2o/latest-stable/h2o-docs/automl.html

Sources:
## CR:

[FINAL SRT FILES – Google Drive](https://drive.google.com/drive/folders/0B5QJULzu8Dw7RHVwVS1yeDczVzg)

[GitHub - RevanthRameshkumar/CRD3: The repo containing the Critical Role Dungeons and Dragons Dataset.](https://github.com/RevanthRameshkumar/CRD3)